Global optimization method with dual Lipschitz constant estimates for problems with non-convex constraints

### 2020-01-31 2019/NUMTA_Barkalov/SoftComputing/article.tex
Fixed several formulas

% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{lineno,hyperref}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

	It is supposed that the objective function $\varphi(y)$ (henceforth denoted by $g_{m+1}(y)$) and the left-hand sides $g_{j}(y), 1 \leq j \leq m$, of the constraints satisfy the Lipschitz condition
\begin{equation}\label{lipschitz_condition}
	\left|g_j(y')-g_j (y'')\right| \leq L_j \|y'-y''\|, \; y', y''\in D, \; 1\leq j \leq m+1,
\end{equation}
with a priori unknown constants $L_j, 1\leq j \leq m+1$, and may be multiextremal.

@@

	Along with the exact solution $y^\ast$ of the problem (\ref{problem}), we will consider also the $\varepsilon$-reserved solution $y_{\epsilon}$, for which 
\begin{equation}\label{epsilon_reserved_solution}
	\varphi(y_{\epsilon})=\min{\left\{\varphi(y):y \in D, \; g_j(y)\leq -{\epsilon}_j, \; 1 \leq j \leq m\right\}},
\end{equation}
and the set of solutions $Y_{\epsilon}$, which are not worse than the $\varepsilon$-reserved solution in the objective function value, i.e.
\begin{equation}\label{Y_epsilon}
	Y_{\epsilon}=\left\{ y \in D, \; g_j(y) \leq 0, \; 1 \leq j \leq m, \; \varphi(y) \leq \varphi(y_{\epsilon}) \right\}.
\end{equation}
Fig. \ref{fig:eps_reserved_solution} illustrates the concepts introduced.

@@

	We will consider the initial problem (\ref{problem}) assuming that the problem functions $g_{j}(y), 1 \leq j \leq m+1,$ may be defined only partly. It means that they are defined and computable only in the sets 
\begin{equation}\label{D_sets}
	D_1 = D, \; D_{j+1} = \left\{ y \in D_j: \; g_j(y) \leq 0 \right\}, \; 1 \leq j \leq m.
\end{equation}
This situation is typical for the optimal design problems when some conditions for the functioning of the modeled object are not met and its other characteristics appear to be undefined. In this approach, the first violation of any constraint indicating that the point $y$ being considered is no longer feasible terminates further computations at the point $y$.

	Many well known approaches to solving the multidimensional global optimization problems are based on either explicit or implicit reduction of multidimensional problems to one-dimensional ones (see, for example, the description of methods using the diagonal partitions \cite{Sergeyev2006} or simplicial partitions \cite{Zilinskas2008}). In this paper, we will use the approach based on the dimensionality reduction with the use of the space-filling curve $y(x)$ (the Peano curve). Continuous unambiguous mapping $y(x)$ projecting the interval [0,1] onto an $N$-dimensional hypercube $D$ allows reducing a multidimensional constrained minimization problem in the domain $D$ to a one-dimensional constrained optimization problem in the interval [0,1]
\begin{equation}\label{one_dimensional_problem}
	\varphi(y(x^\ast))=\min \left\{\varphi(y(x)): x \in [0,1], \; g_j(y(x))\leq 0, \; 1 \leq j \leq m\right\}.
\end{equation}
The issues of the numerical construction of the Peano space filling curve-type mappings and the corresponding theory were described in detail in \cite{Strongin2000,Sergeyev2013}. Note that the theoretical Peano curve $y(x)$ is a limit object and in practice is replaced by its approximation (called \textit{evolvent}) with predefined precision $2^{-m}$, where the number $m>1$ is a parameter (the \textit{density} of the evolvent). The evolvent density is determined by the accuracy of the possible practical implementation of the problem solution found. For  illustration, Fig. \ref{fig:evolvent} (a), (b) shows the projections of the interval $[0,1]$ for the mapping $y(x)$ with $N=2$ and $m=4,5$, correspondingly.
\begin{figure}
	\begin{minipage}[h]{0.45\linewidth}
		\center{\includegraphics[width=1.0\linewidth]{evolvent_N=2_m=4} \\ {\footnotesize(a)}}
	\end{minipage}
	\hfill
	\begin{minipage}[h]{0.45\linewidth}
		\center{\includegraphics[width=1.0\linewidth]{evolvent_N=2_m=5} \\ {\footnotesize(b)}}
	\end{minipage}
	\caption{Evolvent for $N=2$ and $m=4$ (a), $m=5$ (b)}
	\label{fig:evolvent}
\end{figure}

	The dimensionality reduction scheme considered here matches a multidimensional problem with Lipschitzian objective function and Lipschitzian constraints to a one-dimensional problem, in which the corresponding functions satisfy the uniform H\"{o}lder condition (see \cite{Strongin2000,Sergeyev2013})
$$
	\left|g_j(y(x'))-g_j(y(x''))\right| \leq K_j \left|x'-x'' \right|^{1/N}, \; x', x''\in [0,1], \; 1\leq j \leq m+1,
$$
where $N$ is the dimensionality of the initial multidimensional problem and the coefficients $K_j$ are related to the Lipschitz constants $L_j$ of the initial problem by the relations
\begin{equation}\label{K_leq_L}
	K_j \leq 2L_j \sqrt{N+3}, \; 1\leq j \leq m+1.
\end{equation}

	According to (\ref{D_sets}) and (\ref{one_dimensional_problem}), the reduced one-dimensional functions $g_j (y(x)), 1 \leq j \leq m+1,$ will also be defined and computable in the corresponding intervals 
\begin{equation}\label{Q_intervals}
	Q_1=[0,1], \; Q_{j+1}=\left\{x \in Q_j : g_j(y(x)) \leq 0 \right\}, \; 1 \leq j \leq m.
\end{equation}
These relations allow introducing a classification of the points $x \in [0,1]$ according to the number $\nu = \nu(x)$ of the constraints computable at the given point. We will call this number $\nu = \nu(x)$ the \textit{index} of the point $x$. The index can be determined from the conditions 
$$
	g_j(y(x)) \leq 0, \; 1 \leq j \leq \nu-1, \; g_{\nu}(y(x))>0,
$$
where the last inequality is insufficient if $\nu = m+1$.

@@

	The main idea of the index scheme of accounting for the constraints consists in the reduction of the constrained problem (\ref{one_dimensional_problem}) (the functions of which satisfy the H\"{o}lder condition with corresponding coefficients $K_j$) to an unconstrained problem of the form
\begin{equation}\label{reduction_problem}
	\psi(x^*)=\min \left\{\psi(x): x \in [0,1] \right\},
\end{equation}
\begin{eqnarray} \nonumber
	\psi(x)=\frac{g_{\nu}(y(x))}{K_{\nu}} - 
	\left\{
   \begin{array}{lr}
     0, & \nu \leq m,\\
     \frac{\varphi^\ast}{K_{m+1}}, & \nu = m + 1,
   \end{array}
	\right.
\end{eqnarray}
where $\nu = \nu(x)$ and $\varphi^\ast$ is the objective function value at the point of the problem solution (\ref{one_dimensional_problem}).

@@

	Determine the maximum value of the index 
$$
	M=\max\left\{\nu=\nu(x_i), \; 1 \leq i \leq k \right \}.
$$ \\
Step 3. Compute the current lower bounds
\begin{equation}\label{current_lower_bounds}
	\mu_{\nu} = \max\left\{ \frac{\left|z_i-z_j\right|}{ (x_i - x_j)^{1/N} }, \; i,j \in I_\nu, \; i>j \right\}
\end{equation}
for the unknown H\"{o}lder constants $K_{\nu}$ of the functions $g_{\nu}, 1 \leq \nu \leq m+1$. If the set $I_{\nu}$ includes less than two elements or if $\mu_{\nu}$ appears to be equal to zero, then set $\mu_{\nu}=1$. \\
Step 4. For all nonempty sets $I_{\nu}, 1 \leq \nu \leq m+1$, compute the estimates
\begin{equation}\label{z_estimates}
	z_\nu^\ast = \left\{
   \begin{array}{lr}
     -\epsilon_\nu, & \nu < M,\\
     \min\{ z_i: i\in I_\nu \}, & \nu = M,
   \end{array}
	\right.
\end{equation}
where the nonnegative numbers $(\epsilon_1,\ldots,\epsilon_m )$ are the algorithm parameters. \\
Step 5. For each interval $(x_{i-1}, x_i), 1 \leq i \leq k+1$, compute the \textit{characteristics} $R(i)$:
\begin{equation}\label{R_1}
	R(i)=\Delta_i+\frac{(z_i-z_{i-1})^2}{r_\nu^2 \mu_\nu^2\Delta_i}-2\frac{z_i+z_{i-1}-2z_\nu^\ast}{r_\nu \mu_\nu}, \;  \nu=\nu(x_i)=\nu(x_{i-1}),
\end{equation}
\begin{equation}\label{R_2}
	R(i)=2\Delta_i-4\frac{z_i-z_\nu^\ast}{r_\nu \mu_\nu}, \; \nu=\nu(x_i)>\nu(x_{i-1}),
\end{equation}
\begin{equation}\label{R_3}
R(i)=2\Delta_i-4\frac{z_{i-1}-z_\nu^\ast}{r_\nu \mu_\nu}, \; \nu=\nu(x_{i-1})>\nu(x_i),
\end{equation}
where $\Delta_i=(x_i-x_{i-1})^{1/N}$. The values $r_{\nu} > 1, 1 \leq \nu \leq m+1$, are the parameters of the algorithm. With an appropriate selection of $r_{\nu}$ one can use the product $r_{\nu}\mu_{\nu}$ as an estimate of H\"{o}lder constants $K_{\nu}, 1 \leq \nu \leq m+1$. \\
Step 6. Find the interval $(x_{t-1}, x_t)$ with the maximum characteristic
\begin{equation}\label{MaxR}
	R(t)=\max{\left\{R(i): 1 \leq i \leq k+1\right\}}.
\end{equation} 
Step 7. Execute the next trial at the middle point of the interval $(x_{t-1}, x_t)$ if the indices of the points $x_{t-1}, x_t$ are not the same, i.e.,
$$
	x^{k+1} = \frac{x_t + x_{t-1}}{2}, \; \nu(x_{t-1}) \neq \nu(x_t).
$$
Otherwise, execute a trial at the point
$$
	x^{k+1} = \frac{x_t+x_{t-1}}{2} + \frac{\mathrm{sign}(z_t-z_{t-1})}{2r_\nu}\left[\frac{\left|z_t-z_{t-1}\right|}{\mu_\nu}\right]^N, \; \nu=\nu(x_{t-1})=\nu(x_t).
$$
The inequality $\Delta_t \leq \epsilon$ can be taken as the termination condition, where $t$ is from (\ref{MaxR}) and $\epsilon>0$ is the predefined accuracy.

	The convergence conditions for the index global search algorithm can be formulated in the form of the following theorem from \cite{Strongin2000}. 
\\
\textbf{Theorem 1}. Assume that the following conditions are satisfied:
\begin{enumerate} 
  \item Problem (\ref{problem}) has an $\varepsilon$-reserved solution $y_{\varepsilon}$ from (\ref{epsilon_reserved_solution}).
  \item Functions $g_j(y), 1 \leq j \leq m+1,$ admit Lipschitzian (with the constants $L_j$) extensions $G_{j}(y)$ over the whole feasible domain $D$ from (\ref{D}), i.e.
$$
	g_j \left( y(x) \right) = G_j \left( y(x) \right), \; x \in Q_j, \; 1 \leq j \leq m+1,
$$
where the sets $Q_j$ are from (\ref{Q_intervals}), and $y(x)$ is the curve from (\ref{one_dimensional_problem}).
	\item The parameters of the method $\epsilon_{\nu}, 1 \leq \nu \leq m,$ used in the rule (\ref{z_estimates}) are the corresponding components of the reserve vector $\epsilon_{R}$ from (\ref{epsilon_reserved_solution}).
	\item For a sufficiently large iteration number $k$, the values $\mu_{\nu}$ from (\ref{current_lower_bounds}) satisfy the inequalities
		\begin{equation}\label{theorem_inequalities}
			r_{\nu}\mu_{\nu} > 2^{3-\frac{1}{N}}L_{\nu}\sqrt{N+3}, \; 1 \leq \nu \leq m+1. 
		\end{equation}
Then, any limit point $\bar{y}$ of the sequence of the trials $\{y^k\}=\big\{y\big(x^k\big)\big\}$ generated by the index algorithm for problem (\ref{problem}) belongs to the set $Y_{\epsilon}$ form (\ref{Y_epsilon}) and satisfies the conditions	
$$
	\varphi(\bar y) = \inf\left\{\varphi(y^k):g_j(y^k) \leq 0, 1 \leq j \leq m, k = 1,2,\ldots \right\} \leq \varphi(y_{\epsilon}).
$$
\end{enumerate}
\textbf{Note 1}. The computational scheme of the algorithm is described in the form convenient for  formulating its theoretical properties. The software implementation of this scheme may be made more frugal. For example, according to Step 7, the point $x^{k+1}$ of the next trial will be an internal point of the interval $(x_{t-1}, x_t)$, i.e. $x^{k+1} \in (x_{t-1}, x_t)$. Therefore, the set of trial points $x^1,\ldots, x^k$ (and the related trial results (\ref{trial_result})) may not be ordered  at every step of the algorithm but may be maintained in an ordered state using appropriate data structures.
\\
\textbf{Note 2}. The use of the set of parameters $\epsilon_1,\ldots,\epsilon_m$ (the values of which correspond to the coordinates of the reserve vector $\epsilon_R$) in the index algorithm will significantly reduce the density of the trial sequence in the vicinity of the feasible domain boundaries. However, this raises a question about the particular values of the reserve vector components $\epsilon_R$. In \cite{Strongin2000}, it was proposed to choose the components of the vector $\epsilon_R$ according to the formula 
\begin{equation}\label{epsilon_nu}
	\epsilon_{\nu} = \mu_{\nu}\delta, \; 1 \leq \nu \leq m, 
\end{equation}
where $\mu_{\nu}$ are the current estimates from (\ref{current_lower_bounds}) and $\delta>0$ is a parameter. This approach to choosing the reserve vector components allows one to take into account the properties of different problem functions characterized by their Lipschitz constants. This method for choosing the reserve vector was used in the numerical experiments, the results of which are presented below.
\\
\textbf{Note 3}. The index algorithm for solving the constrained problems is based on the information-statistical algorithm of global search (AGS) for solving unconstrained problems. AGS has been compared repeatedly with both deterministic and nature-inspired global optimization algorithms. The results of the experimental comparison (see, for example, \cite{Sovrasov2019}) show that AGS is superior to many known methods of similar purpose, including DIRECT and DIRECT\textit{l}.

@@

	\textbf{Proof}. Let us consider two possible cases of the values of the indices $\nu(x_{i-1})$ and $\nu(x_i)$. 
\begin{enumerate} 
  \item If $\nu(x_{i-1}) \neq \nu(x_i)$, then according to  formulae (\ref{R_2}), (\ref{R_3}) 
\begin{equation}\label{R_glob_1}
	R(i)=R_{glob}(i)=R_{loc}(i)=2\Delta_i>0. 
\end{equation}
  \item If $\nu(x_{i-1}) = \nu(x_i) = M$, then, taking into account (\ref{current_lower_bounds}), the following inequality will hold
$$
	z_i+z_{i-1}-2z_M^* = |z_i-z_{i-1}|\leq \mu_M\Delta_i .
$$
\end{enumerate}
From here, it will follow that for any value $r_M>1$ the following inequalities will hold
\begin{eqnarray}
	R(i) & = & \Delta_i + \frac{(z_i-z_{i-1})^2}{r_M^2\mu_M^2\Delta_i} - 2\frac{z_i+z_{i-1}-2z_M^*}{r_M\mu_M} \geq \Delta_i + \frac{(z_i-z_{i-1})^2}{r_M^2\mu_M^2\Delta_i} - 2\frac{\mu_M\Delta_i}{r_M\mu_M} \nonumber \\
	& \geq & \Delta_i + \frac{(z_i-z_{i-1})^2}{r_M^2\mu_M^2\Delta_i} - 2\frac{\Delta_i}{r_M} = \Delta_i + \Delta_i\frac{(z_i-z_{i-1})^2/\Delta_i^2}{r_M^2\mu_M^2\Delta_i^2} - 2\frac{\Delta_i}{r_M}
\nonumber \\
	& \geq & \Delta_i + \frac{\Delta_i}{r_M^2} - 2\frac{\Delta_i}{r_M} = \Delta_i \left( 1-\frac{1}{r_M} \right)^2>0.
	\nonumber
\end{eqnarray}
And because $r_{M}^{glob} > r_{M}^{loc} > 1$, then
\begin{equation}\label{R_glob_greater_R_loc}
	R_{glob}(i)=\Delta_i\left(1-\frac{1}{r_M^{glob}} \right)^2 > \Delta_i\left(1-\frac{1}{r_M^{loc}} \right)^2 = R_{loc}(i).
\end{equation}
The statement is proved.

>>>>

\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{lineno,hyperref,amsmath}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

	It is supposed that the objective function $\varphi(y)$ (henceforth denoted by $g_{m+1}(y)$) and the left-hand sides $g_{j}(y), 1 \leq j \leq m$, of the constraints satisfy the Lipschitz condition
\begin{align}\label{lipschitz_condition}
	\left|g_j(y')-g_j (y'')\right| \leq L_j \|y'-y''\|, \nonumber \\ 
	y', y''\in D, \; 1\leq j \leq m+1,
\end{align}
with a priori unknown constants $L_j, 1\leq j \leq m+1$, and may be multiextremal.

@@

	Along with the exact solution $y^\ast$ of the problem (\ref{problem}), we will consider also the $\varepsilon$-reserved solution $y_{\epsilon}$, for which 
\begin{align}\label{epsilon_reserved_solution}
	\varphi(y_{\epsilon}) &= \nonumber \\
	&\min{\left\{\varphi(y):y \in D, g_j(y)\leq -{\epsilon}_j, 1 \leq j \leq m\right\}},
\end{align}
and the set of solutions $Y_{\epsilon}$, which are not worse than the $\varepsilon$-reserved solution in the objective function value, i.e.
\begin{align}\label{Y_epsilon}
	Y_{\epsilon} &= \nonumber \\
	&\left\{ y \in D, \; g_j(y) \leq 0, \; 1 \leq j \leq m, \; \varphi(y) \leq \varphi(y_{\epsilon}) \right\}.
\end{align}
Fig. \ref{fig:eps_reserved_solution} illustrates the concepts introduced.

@@

	We will consider the initial problem (\ref{problem}) assuming that the problem functions $g_{j}(y), 1 \leq j \leq m+1,$ may be defined only partly. It means that they are defined and computable only in the sets 
\begin{align}\label{D_sets}
	D_1 = D, \; D_{j+1} = \left\{ y \in D_j: \; g_j(y) \leq 0 \right\}, \nonumber \\
	1 \leq j \leq m.
\end{align}
This situation is typical for the optimal design problems when some conditions for the functioning of the modeled object are not met and its other characteristics appear to be undefined. In this approach, the first violation of any constraint indicating that the point $y$ being considered is no longer feasible terminates further computations at the point $y$.

	Many well known approaches to solving the multidimensional global optimization problems are based on either explicit or implicit reduction of multidimensional problems to one-dimensional ones (see, for example, the description of methods using the diagonal partitions \cite{Sergeyev2006} or simplicial partitions \cite{Zilinskas2008}). In this paper, we will use the approach based on the dimensionality reduction with the use of the space-filling curve $y(x)$ (the Peano curve). Continuous unambiguous mapping $y(x)$ projecting the interval [0,1] onto an $N$-dimensional hypercube $D$ allows reducing a multidimensional constrained minimization problem in the domain $D$ to a one-dimensional constrained optimization problem in the interval [0,1]
\begin{align}\label{one_dimensional_problem}
	\varphi(y(x^\ast)) =  
	\min \left\{\varphi(y(x)): x \in [0,1], \; g_j(y(x))\leq 0, \; 1 \leq j \leq m\right\}.
\end{align}
The issues of the numerical construction of the Peano space filling curve-type mappings and the corresponding theory were described in detail in \cite{Strongin2000,Sergeyev2013}. Note that the theoretical Peano curve $y(x)$ is a limit object and in practice is replaced by its approximation (called \textit{evolvent}) with predefined precision $2^{-m}$, where the number $m>1$ is a parameter (the \textit{density} of the evolvent). The evolvent density is determined by the accuracy of the possible practical implementation of the problem solution found. For  illustration, Fig. \ref{fig:evolvent} (a), (b) shows the projections of the interval $[0,1]$ for the mapping $y(x)$ with $N=2$ and $m=4,5$, correspondingly.
\begin{figure}
	\begin{minipage}[h]{0.45\linewidth}
		\center{\includegraphics[width=1.0\linewidth]{evolvent_N=2_m=4} \\ {\footnotesize(a)}}
	\end{minipage}
	\hfill
	\begin{minipage}[h]{0.45\linewidth}
		\center{\includegraphics[width=1.0\linewidth]{evolvent_N=2_m=5} \\ {\footnotesize(b)}}
	\end{minipage}
	\caption{Evolvent for $N=2$ and $m=4$ (a), $m=5$ (b)}
	\label{fig:evolvent}
\end{figure}

	The dimensionality reduction scheme considered here matches a multidimensional problem with Lipschitzian objective function and Lipschitzian constraints to a one-dimensional problem, in which the corresponding functions satisfy the uniform H\"{o}lder condition (see \cite{Strongin2000,Sergeyev2013})
\begin{align*} 
	\left|g_j(y(x'))-g_j(y(x''))\right| \leq K_j \left|x'-x'' \right|^{1/N}, \\  
	x', x''\in [0,1], \; 1\leq j \leq m+1,
\end{align*}
where $N$ is the dimensionality of the initial multidimensional problem and the coefficients $K_j$ are related to the Lipschitz constants $L_j$ of the initial problem by the relations
\begin{equation}\label{K_leq_L}
	K_j \leq 2L_j \sqrt{N+3}, \; 1\leq j \leq m+1.
\end{equation}

	According to (\ref{D_sets}) and (\ref{one_dimensional_problem}), the reduced one-dimensional functions $g_j (y(x)), 1 \leq j \leq m+1,$ will also be defined and computable in the corresponding intervals 
\begin{align}\label{Q_intervals}
	Q_1=[0,1], \; Q_{j+1}=\left\{x \in Q_j : g_j(y(x)) \leq 0 \right\}, \nonumber \\
	1 \leq j \leq m.
\end{align}
These relations allow introducing a classification of the points $x \in [0,1]$ according to the number $\nu = \nu(x)$ of the constraints computable at the given point. We will call this number $\nu = \nu(x)$ the \textit{index} of the point $x$. The index can be determined from the conditions 
$$
	g_j(y(x)) \leq 0, \; 1 \leq j \leq \nu-1, \; g_{\nu}(y(x))>0,
$$
where the last inequality is insufficient if $\nu = m+1$.

@@

	The main idea of the index scheme of accounting for the constraints consists in the reduction of the constrained problem (\ref{one_dimensional_problem}) (the functions of which satisfy the H\"{o}lder condition with corresponding coefficients $K_j$) to an unconstrained problem of the form
\begin{equation}\label{reduction_problem}
	\psi(x^*)=\min \left\{\psi(x): x \in [0,1] \right\},
\end{equation}
\begin{eqnarray*}
	\psi(x)=\frac{g_{\nu}(y(x))}{K_{\nu}} - 
	\left\{
   \begin{array}{lr}
     0, & \nu \leq m,\\
     \frac{\varphi^\ast}{K_{m+1}}, & \nu = m + 1,
   \end{array}
	\right.
\end{eqnarray*}
where $\nu = \nu(x)$ and $\varphi^\ast$ is the objective function value at the point of the problem solution (\ref{one_dimensional_problem}).

@@

	Determine the maximum value of the index 
$$
	M=\max\left\{\nu=\nu(x_i), \; 1 \leq i \leq k \right \}.
$$ \\
Step 3. Compute the current lower bounds
\begin{equation}\label{current_lower_bounds}
	\mu_{\nu} = \max\left\{ \frac{\left|z_i-z_j\right|}{ (x_i - x_j)^{1/N} }, \; i,j \in I_\nu, \; i>j \right\}
\end{equation}
for the unknown H\"{o}lder constants $K_{\nu}$ of the functions $g_{\nu}, 1 \leq \nu \leq m+1$. If the set $I_{\nu}$ includes less than two elements or if $\mu_{\nu}$ appears to be equal to zero, then set $\mu_{\nu}=1$. \\
Step 4. For all nonempty sets $I_{\nu}, 1 \leq \nu \leq m+1$, compute the estimates
\begin{equation}\label{z_estimates}
	z_\nu^\ast = \left\{
   \begin{array}{lr}
     -\epsilon_\nu, & \nu < M,\\
     \min\{ z_i: i\in I_\nu \}, & \nu = M,
   \end{array}
	\right.
\end{equation}
where the nonnegative numbers $(\epsilon_1,\ldots,\epsilon_m )$ are the algorithm parameters. \\
Step 5. For each interval $(x_{i-1}, x_i), 1 \leq i \leq k+1$, compute the \textit{characteristics} $R(i)$:
\begin{align}\label{R_1}
	R(i)=\Delta_i+\frac{(z_i-z_{i-1})^2}{r_\nu^2 \mu_\nu^2\Delta_i}-2\frac{z_i+z_{i-1}-2z_\nu^\ast}{r_\nu \mu_\nu}, \nonumber \\ 
 \nu=\nu(x_i)=\nu(x_{i-1}),
\end{align}
\begin{equation}\label{R_2}
	R(i)=2\Delta_i-4\frac{z_i-z_\nu^\ast}{r_\nu \mu_\nu}, \; \nu=\nu(x_i)>\nu(x_{i-1}),
\end{equation}
\begin{equation}\label{R_3}
R(i)=2\Delta_i-4\frac{z_{i-1}-z_\nu^\ast}{r_\nu \mu_\nu}, \; \nu=\nu(x_{i-1})>\nu(x_i),
\end{equation}
where $\Delta_i=(x_i-x_{i-1})^{1/N}$. The values $r_{\nu} > 1, 1 \leq \nu \leq m+1$, are the parameters of the algorithm. With an appropriate selection of $r_{\nu}$ one can use the product $r_{\nu}\mu_{\nu}$ as an estimate of H\"{o}lder constants $K_{\nu}, 1 \leq \nu \leq m+1$. \\
Step 6. Find the interval $(x_{t-1}, x_t)$ with the maximum characteristic
\begin{equation}\label{MaxR}
	R(t)=\max{\left\{R(i): 1 \leq i \leq k+1\right\}}.
\end{equation} 
Step 7. Execute the next trial at the middle point of the interval $(x_{t-1}, x_t)$ if the indices of the points $x_{t-1}, x_t$ are not the same, i.e.,
$$
	x^{k+1} = \frac{x_t + x_{t-1}}{2}, \; \nu(x_{t-1}) \neq \nu(x_t).
$$
Otherwise, execute a trial at the point
\begin{align*}
	x^{k+1} = \frac{x_t+x_{t-1}}{2} + \frac{\mathrm{sign}(z_t-z_{t-1})}{2r_\nu}\left[\frac{\left|z_t-z_{t-1}\right|}{\mu_\nu}\right]^N, \; \\
	\nu=\nu(x_{t-1})=\nu(x_t).
\end{align*}
The inequality $\Delta_t \leq \epsilon$ can be taken as the termination condition, where $t$ is from (\ref{MaxR}) and $\epsilon>0$ is the predefined accuracy.

	The convergence conditions for the index global search algorithm can be formulated in the form of the following theorem from \cite{Strongin2000}. 
\\
\textbf{Theorem 1}. Assume that the following conditions are satisfied:
\begin{enumerate} 
  \item Problem (\ref{problem}) has an $\varepsilon$-reserved solution $y_{\varepsilon}$ from (\ref{epsilon_reserved_solution}).
  \item Functions $g_j(y), 1 \leq j \leq m+1,$ admit Lipschitzian (with the constants $L_j$) extensions $G_{j}(y)$ over the whole feasible domain $D$ from (\ref{D}), i.e.
$$
	g_j \left( y(x) \right) = G_j \left( y(x) \right), \; x \in Q_j, \; 1 \leq j \leq m+1,
$$
where the sets $Q_j$ are from (\ref{Q_intervals}), and $y(x)$ is the curve from (\ref{one_dimensional_problem}).
	\item The parameters of the method $\epsilon_{\nu}, 1 \leq \nu \leq m,$ used in the rule (\ref{z_estimates}) are the corresponding components of the reserve vector $\epsilon_{R}$ from (\ref{epsilon_reserved_solution}).
	\item For a sufficiently large iteration number $k$, the values $\mu_{\nu}$ from (\ref{current_lower_bounds}) satisfy the inequalities
		\begin{equation}\label{theorem_inequalities}
			r_{\nu}\mu_{\nu} > 2^{3-\frac{1}{N}}L_{\nu}\sqrt{N+3}, \; 1 \leq \nu \leq m+1. 
		\end{equation}
Then, any limit point $\bar{y}$ of the sequence of the trials $\{y^k\}=\big\{y\big(x^k\big)\big\}$ generated by the index algorithm for problem (\ref{problem}) belongs to the set $Y_{\epsilon}$ form (\ref{Y_epsilon}) and satisfies the conditions	
\end{enumerate}
\begin{eqnarray*}
	\varphi(\bar y) =	\inf\left\{\varphi(y^k):g_j(y^k) \leq 0, 1 \leq j \leq m, k = 1,2,\ldots \right\} \\ \leq \varphi(y_{\epsilon}).
\end{eqnarray*}
\textbf{Note 1}. The computational scheme of the algorithm is described in the form convenient for  formulating its theoretical properties. The software implementation of this scheme may be made more frugal. For example, according to Step 7, the point $x^{k+1}$ of the next trial will be an internal point of the interval $(x_{t-1}, x_t)$, i.e. $x^{k+1} \in (x_{t-1}, x_t)$. Therefore, the set of trial points $x^1,\ldots, x^k$ (and the related trial results (\ref{trial_result})) may not be ordered  at every step of the algorithm but may be maintained in an ordered state using appropriate data structures.
\\
\textbf{Note 2}. The use of the set of parameters $\epsilon_1,\ldots,\epsilon_m$ (the values of which correspond to the coordinates of the reserve vector $\epsilon_R$) in the index algorithm will significantly reduce the density of the trial sequence in the vicinity of the feasible domain boundaries. However, this raises a question about the particular values of the reserve vector components $\epsilon_R$. In \cite{Strongin2000}, it was proposed to choose the components of the vector $\epsilon_R$ according to the formula 
\begin{equation}\label{epsilon_nu}
	\epsilon_{\nu} = \mu_{\nu}\delta, \; 1 \leq \nu \leq m, 
\end{equation}
where $\mu_{\nu}$ are the current estimates from (\ref{current_lower_bounds}) and $\delta>0$ is a parameter. This approach to choosing the reserve vector components allows one to take into account the properties of different problem functions characterized by their Lipschitz constants. This method for choosing the reserve vector was used in the numerical experiments, the results of which are presented below.
\\
\textbf{Note 3}. The index algorithm for solving the constrained problems is based on the information-statistical algorithm of global search (AGS) for solving unconstrained problems. AGS has been compared repeatedly with both deterministic and nature-inspired global optimization algorithms. The results of the experimental comparison (see, for example, \cite{Sovrasov2019}) show that AGS is superior to many known methods of similar purpose, including DIRECT and DIRECT\textit{l}.

@@

	\textbf{Proof}. Let us consider two possible cases of the values of the indices $\nu(x_{i-1})$ and $\nu(x_i)$. 
\begin{enumerate} 
  \item If $\nu(x_{i-1}) \neq \nu(x_i)$, then according to  formulae (\ref{R_2}), (\ref{R_3}) 
\begin{equation}\label{R_glob_1}
	R(i)=R_{glob}(i)=R_{loc}(i)=2\Delta_i>0. 
\end{equation}
  \item If $\nu(x_{i-1}) = \nu(x_i) = M$, then, taking into account (\ref{current_lower_bounds}), the following inequality will hold
$$
	z_i+z_{i-1}-2z_M^* = |z_i-z_{i-1}|\leq \mu_M\Delta_i .
$$
\end{enumerate}
From here, it will follow that for any value $r_M>1$ the following inequalities will hold
\begin{align}
	R(i) & = \Delta_i + \frac{(z_i-z_{i-1})^2}{r_M^2\mu_M^2\Delta_i} - 2\frac{z_i+z_{i-1}-2z_M^*}{r_M\mu_M} \nonumber \\
	& \geq  \Delta_i + \frac{(z_i-z_{i-1})^2}{r_M^2\mu_M^2\Delta_i} - 2\frac{\mu_M\Delta_i}{r_M\mu_M} \nonumber \\
  & \geq \Delta_i + \frac{(z_i-z_{i-1})^2}{r_M^2\mu_M^2\Delta_i} - 2\frac{\Delta_i}{r_M} \nonumber \\
	& = \Delta_i + \Delta_i\frac{(z_i-z_{i-1})^2/\Delta_i^2}{r_M^2\mu_M^2\Delta_i^2} - 2\frac{\Delta_i}{r_M} \nonumber \\
	& \geq \Delta_i + \frac{\Delta_i}{r_M^2} - 2\frac{\Delta_i}{r_M} = \Delta_i \left( 1-\frac{1}{r_M} \right)^2>0.
\end{align}
And because $r_{M}^{glob} > r_{M}^{loc} > 1$, then
\begin{align}\label{R_glob_greater_R_loc}
	R_{glob}(i) & = \Delta_i\left(1-\frac{1}{r_M^{glob}} \right)^2 \nonumber \\
	& > \Delta_i\left(1-\frac{1}{r_M^{loc}} \right)^2 = R_{loc}(i).
\end{align}
The statement is proved.
